Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-11-11 paper/paper.tex
comment out \ja in introduction

\ja{This section is way too long.
It's important that we situate ourselves with respect to the existing literature, but we don't need to spend 2+ pages doing so.
This currently reads more like a laundry list of various work related to timbre perception on musical instruments on one hand and a history of STRFs on the other.
We need to keep in mind what our central themes (wider range of timbre, similarity-based evaluation, simple scattering+linear model) are and link the existing work to them in a concise manner.
}

>>>>

%\ja{This section is way too long.
%It's important that we situate ourselves with respect to the existing literature, but we don't need to spend 2+ pages doing so.
%This currently reads more like a laundry list of various work related to timbre perception on musical instruments on one hand and a history of STRFs on the other.
%We need to keep in mind what our central themes (wider range of timbre, similarity-based evaluation, simple scattering+linear model) are and link the existing work to them in a concise manner.
%}
